Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
Tilbakemelding fra Audun
Biblografistyle

benchmarking for optimization


git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@80 43ef1190-90fd-4dd7-a769-d0121f02b80e
Tilbakemelding fra Audun
kommenter små forskjeller


git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@81 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

Using techniques from statistical experimental design, I propose
that it is possible to design an experiment (i.e. a benchmark) so that
we can prove it covers all realistic cases and that we can justify
why the remaining corner cases are unlikely to influence the result.

@@

@@

\bibliographystyle{plain}
\bibliography{selectivity,federation,benchmarks,optimization}

>>>>

These small differences may become important if they are systematic,
even if one engine is dramatically better than another in one case,
small deficiencies may add up to make the other a better choice for
most applications anyway.

@@

Using techniques from statistical experimental design, I propose
that it is possible to design an experiment (i.e. a benchmark) so that
we can prove it covers all realistic cases and that we can justify
why the remaining corner cases are unlikely to influence the
result. For further elaboration, see Section~\ref{sec:benchmethod}.

Thus far, the benchmarking problem has been seen as a software testing
problem, but we could also ask if the existence of benchmark data can
be exposed to help federation query optimizers along with a
statistical digest.

@@

\subsection{In Benchmarking}\label{sec:benchmethod}

@@

%\bibliographystyle{plain}
\bibliographystyle{plain-csmin}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}
